Field-informed Reinforcement Learning for Learning Large Scale Collective Tasks

### 2023-05-03 paper.tex
chore: minor on title
chore: on intro

\usepackage{cleveref}
\lstset{language=Pascal}
\begin{document}
%
\title{Field-informed Reinforcement Learning for Learnining Large Scale Collective Tasks} %% Todo improve
% or: Field-Informed Reinforcement Learning: A Scalable and Effective Method for Collective Intelligence
% or: A Novel Approach to Reinforcement Learning for Adaptive Collective Systems
%

@@

%%% Comment command, to be removed before submission
\newcommand{\meta}[3]{\textcolor{#1}{\textbf{#2}: #3}}
\newcommand{\ga}[1]{\meta{red}{GA}{#1}}
\newcommand{\lukas}[1]{\meta{purple}{Lukas}{#1}}
\newcommand{\mv}[1]{\meta{green}{MV}{#1}}
%% ACRONYMS
\acrodef{DecPOMDP}[DecPOMDP]{decentralized partially observable Markov decision processes}
\acrodef{RL}[RL]{reinforcement learning}
\acrodef{MARL}[MARL]{multi-agent reinforcement learning}
\acrodef{MLP}[MLP]{multi-layer perceptron}
\acrodef{GNN}[GNN]{graph neural network}
\acrodef{CNN}[CNN]{convolutional neural network}
\ga{Page limit: 10 pages (include refs)}

@@

In this paper, we propose a novel approach combining aggregate computing
~\cite{Beal2015Computer} with Graph Neural Networks
~\cite{Zhou2020AIOpen} to focus on the relevant areas. We further combine this with reinforcement learning techniques to respond to changing conditions in the environment.
Specifically, we will show... \lukas{more info...}

The remainder of this paper is structured as follows. First, we introduce the relevant background and problem formulation in \Cref{sec:background}. Afterwards, we introduce our approach in Section~\Cref{sec:approach}. Section~\Cref{sec:eval} outlines the performed experiments and discusses the obtained results. Finally, we will present our conclusions in Section~\Cref{sec:conclusion}.

\section{Background and Motivation}
\label{sec:background}
\ga{Page budget: 1/2 page \\}
\ga{Plan: discussion about the problem of coordination in multi-agent systems 
and the need for a scalable approach. In doing this, we will discuss some of the existing approaches (declarative, RL and )}
\subsection{Field Coordination Approaches}
\ga{discussion about field used as a coordination mechanism in multi-agent systems. Introduction to AC}
\subsection{Graph Neural Networks}
Over the years, several different neural networks have been proposed to solve specific tasks, ranging from 
  simple \ac{MLP} to \ac{CNN}~\cite{oshea2015introduction}.
%
Whereas \ac{CNN} is designed to be used with image and spatial-like data (e.g., audio),
 \ac{GNN} is a novel model used to process graph-structured data. 
%
Let $ G = (V, E) $ be a graph, where $ V $ is the set of nodes and $ E $ is the set of edges. 
%
Given $X_v$ a feature vector associated to each node $v \in V$, 
 the goal of a GNN is to learn the node embedding $X'_v$ for each node $v \in V$.
 In modern GNNs, the node embedding $X'_v$ is computed by aggregating information from the node's neighbours $N(v)$,
  and then combining it with the node's current embedding $X_v$.
% 
Formally, a GNN can be defined by two phases:
\begin{equation}
a_{v}^{(k)}=\operatorname{AGGREGATE}^{(k)}\left(\left\{h_{u}^{(k-1)}: u \in \mathcal{N}(v)\right\}\right)   
\end{equation}
\begin{equation}
h_{v}^{(k)}=\operatorname{COMBINE}^{(k)}\left(h_{v}^{(k-1)}, a_{v}^{(k)}\right)
\end{equation}
where $h_{v}^{k}$ is the embedding of node $v$ at the $k$-th layer, 
 $\mathcal{N}(v)$ is the set of neighbors of node $v$ computed from $E$.
%
The differential part come into play in the $\operatorname{COMBINE}$ function, 
 which is usually a differentiable function such as a neural network layer.
%
$\operatorname{AGGREGATE} $ instead is a function that aggregates the information from the neighbours of a node $v$
  and it could be a simple sum or a more complex function such as a neural network layer.
%
This formulation allows GNNs to effectively process and extract features from graph-structured data by iteratively aggregating and transforming information from the node's neighbours.

>>>>

\usepackage{cleveref}
\lstset{language=Pascal}
\begin{document}
%
\title{Field-informed Reinforcement Learning for Learning Large Scale Collective Tasks} %% Todo improve
% or: Field-Informed Reinforcement Learning: A Scalable and Effective Method for Collective Intelligence
% or: A Novel Approach to Reinforcement Learning for Adaptive Collective Systems
%

@@

%%% Comment command, to be removed before submission
\newcommand{\meta}[3]{\textcolor{#1}{\textbf{#2}: #3}}
\newcommand{\ga}[1]{\meta{red}{GA}{#1}}
\newcommand{\lukas}[1]{\meta{purple}{Lukas}{#1}}
\newcommand{\mv}[1]{\meta{green}{MV}{#1}}
%% ACRONYMS
\acrodef{DecPOMDP}[DecPOMDP]{decentralized partially observable Markov decision processes}
\acrodef{RL}[RL]{reinforcement learning}
\acrodef{MARL}[MARL]{multi-agent reinforcement learning}
\acrodef{MAARL}[ManyRL]{many-agent reinforcement learning}

\acrodef{MLP}[MLP]{multi-layer perceptron}
\acrodef{GNN}[GNN]{graph neural network}
\acrodef{CNN}[CNN]{convolutional neural network}
\ga{Page limit: 10 pages (include refs)}

@@

In this paper, we propose a novel approach combining aggregate computing~\cite{Beal2015Computer} with Graph Neural Networks~\cite{Zhou2020AIOpen} to focus on the relevant areas. We further combine this with reinforcement learning techniques to respond to changing conditions in the environment.
%Specifically, we will show... \lukas{more info...}
Specifically, 
 our approach utilizes aggregate computing to disseminate information by manipulating a computational field, 
 which is a distributed data structure that maps devices to information. 
 This field functions as a dynamic environment in which information is continuously updated and diffused throughout the system. 
 By leveraging this layer, we can build collective distributed intelligence using \ac{GNN},
  which uses the information in the field to determine the best action for a given task.
\ga{first draft, need a refinement}
The remainder of this paper is structured as follows. First, we introduce the relevant background and problem formulation in \Cref{sec:background}. Afterwards, we introduce our approach in Section~\Cref{sec:approach}. Section~\Cref{sec:eval} outlines the performed experiments and discusses the obtained results. Finally, we will present our conclusions in Section~\Cref{sec:conclusion}.

\section{Background and Motivation}
Field-based RL draws upon research areas that were not previously considered in traditional RL. 
%
This section provides an overview of three key concepts that underpin this approach, 
 namely 
 field-based coordination --i.e., coordinating multi-agent systems through computational fields--, 
 \ac{GNN} --i.e., a novel type of neural network architecture designed to process graph-structured data--, 
 and \ac{MAARL} ---i.e., a large number of agents learning a collective policy to achieve a global goal.
\label{sec:background}
\ga{Page budget: 1/2 page \\}
\ga{Plan: discussion about the problem of coordination in multi-agent systems 
and the need for a scalable approach. In doing this, we will discuss some of the existing approaches (declarative, RL and )}
\subsection{Field Coordination Approaches}
\ga{discussion about field used as a coordination mechanism in multi-agent systems. Introduction to AC}
\subsection{Graph Neural Networks}
Over the years, several different neural networks have been proposed to solve specific tasks, ranging from 
  simple \ac{MLP} to \ac{CNN}~\cite{oshea2015introduction}.
%
Whereas \ac{CNN} is designed to be used with image and spatial-like data (e.g., audio),
 \ac{GNN} is a novel model used to process graph-structured data. 
%
Let $ G = (V, E) $ be a graph, where $ V $ is the set of nodes and $ E $ is the set of edges. 
%
Given $X_v$ a feature vector associated to each node $v \in V$, 
 the goal of a GNN is to learn the node embedding $X'_v$ for each node $v \in V$.
 In modern GNNs, the node embedding $X'_v$ is computed by aggregating information from the node's neighbours $N(v)$,
  and then combining it with the node's current embedding $X_v$.
% 
Formally, a GNN can be defined by two phases:
\begin{equation}
a_{v}^{(k)}=\operatorname{AGGREGATE}^{(k)}\left(\left\{h_{u}^{(k-1)}: u \in \mathcal{N}(v)\right\}\right)   
\end{equation}
\begin{equation}
h_{v}^{(k)}=\operatorname{COMBINE}^{(k)}\left(h_{v}^{(k-1)}, a_{v}^{(k)}\right)
\end{equation}
where $h_{v}^{k}$ is the embedding of node $v$ at the $k$-th layer, 
 $\mathcal{N}(v)$ is the set of neighbors of node $v$ computed from $E$.
%
The differential part come into play in the $\operatorname{COMBINE}$ function, 
 which is usually a differentiable function such as a neural network layer.
%
$\operatorname{AGGREGATE} $ instead is a function that aggregates the information from the neighbours of a node $v$
  and it could be a simple sum or a more complex function such as a neural network layer.
%
This formulation allows GNNs to effectively process and extract features from graph-structured data by iteratively aggregating and transforming information from the node's neighbours.
